Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-07 paper.tex
Add reference and fix a broken reference
write transform to real circuit

\documentclass{article}
\usepackage{authblk}
\usepackage{amsmath, amssymb, amsthm}

@@

\begin{definition}
	Denote the \emph{controlled phase gate}: $C_\phi|xy\rangle=(-1)^{xy}|xy\rangle$.
\end{definition}

@@

@@

TODO check where does \cite{arXiv:1904.06320} fit in.

@@

@@

The transform is found in \cite{1109.0795}. It turns the states and the unitary matrices into real numbers.

TODO: maybe describe the transform here as needed. Need to show that this doesn't change X/Z measurements. Also need to show that the result of this can still be rewritten into controlled phase gates and one-qubit gates.

@@

>>>>

\documentclass{article}
\usepackage{authblk}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{braket}

@@

@@

\begin{definition}
	Let $\Lambda_c(U)$ denote the gate $U$ controlled on qubit $c$. $\Lambda_{f, s}(U)$ would be the gate $U$ controlled by both $f$ and $s$. I.e. $\Lambda{1, 2}(X_3)$ would be a Toffoli ((CCNOT) gate.
\end{definition}

\begin{definition}
	Let $P(i)=\begin{pmatrix}1&0\\0&i\end{pmatrix}$
\end{definition}

@@

TODO check where does \cite{1904.06320} fit in.

@@

We pick our universal gate set to be Hadamard gate and controlled phase gate:
$$H=\frac{1}{\sqrt{2}}\begin{pmatrix}1&1\\1&-1\end{pmatrix}$$
$$\Lambda(P(i))=\begin{pmatrix}1&0&0&0\\0&1&0&0\\0&0&1&0\\0&0&0&i\end{pmatrix}$$
We know this is universal from (TODO cite Kitaev). So each $U_i\in\set{H, \Lambda(P(i))}$

@@

Here we first reduce the circuit to real gates and states only. The proof is taken from \cite{quant-ph/0301040}.

We consider the transform $T\ket{\psi}=\ket{0}\otimes\Re|\psi\rangle+\ket{1}\otimes\Im\ket{\psi}$, where $\Re$ and $\Im$ denote real and imaginary parts respectively. To simplify some notations, let $\ket{\psi}$ be 1-indexed, and let the added qubit be the 0th. Note that after this transformation, the state is real. This transformation preserves measurement results in the standard basis. Under the transform, Hadamard gates are unchanged, but controlled phase gates become a combination of Hadamard and Toffoli gates. Mathematically,
$$T\circ H_f=H_f\circ T$$
$$T\circ\Lambda_f(P(i)_s)=\Lambda_{f,s}(X_0)\Lambda_{f,s}(Z_0)\circ T=\Lambda_{f,s}(X_0)H_0\Lambda_{f,s}(X_0)H_0\circ T$$

@@

	\bibitem{quant-ph/0301040}
	Dorit Aharonov.
	\newblock A Simple Proof that Toffoli and Hadamard are Quantum Universal, 2003;
	\newblock arXiv:quant-ph/0301040.
